---
title: "Week_6"
author: "Burton Karger"
date: "9/30/2019"
output: html_document
---
Reading Data in
```{r}
library(tidyverse)
country_time <- read_csv("Part_Two/Data/country_timeseries.csv")
head(country_time, n = 3)
mex_deaths <- read_csv("Part_Two/Data/mexico_deaths.csv")
head(mex_deaths, n = 3)
mex_exp <- read_csv("Part_Two/Data/mexico_exposure.csv")
head(mex_exp, n = 3)
```
Joining the data using dplyr *_join (Inner: will only keep things that show up in both data sets, full: everything from either data set[adds NA for items that were in one set that don't exist in the other], left: takes everything from first data set and only pulls things from the other data that matches, right)
```{r}
library(lubridate)
library(ggplot2)
mexico <- full_join(mex_deaths, mex_exp, by = "day") %>% 
  select(day, deaths, temp_mean) %>% 
  mutate(day = mdy(day))

ggplot(data = mexico) +
  geom_point(mapping = aes(x = day, y = deaths), 
             size = 1.4, alpha = 0.5) +
  labs(x = "Date in 2008", y = "# of Deaths") +
  ggtitle("Mexico Data")
  theme_bw()
```
Using pivot_longer, pivot_wider
Get to pick new column names generated by these calls
```{r}
library(tidyr)

```